A Detection of the Environmental Dependence of the Stellar Profiles and haloes of Massive Central Galaxies

### 2017-07-13 draft/paper2.tex
Organzie appendix

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=16.5cm]{fig/redbcg_sample_stats_old}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{B. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{fig/redbcg_prof_gama_new}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.~~
        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
        \nbcg{} (grey-black) galaxies using the samples matched on the 
        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
    \label{fig:gama}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

\section{C. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

%% ------------------------------------------------------------------------------------ %% 
\begin{figure}
    \centering 
    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
    \caption{
        Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
        We show the individual profile in the background using much thinner line, 
        and highlight the median profiles using thicker line and darker color.
        Other formats are exactly the same with the left figure of 
        Fig~\ref{fig:avg_prof}.}
    \label{fig:avg_prof_z}
\end{figure}    
%% ------------------------------------------------------------------------------------ %%

@@

    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
    and compare their \mden{} profiles. 
    In two redshift bins, the median \mden{} profiles from the same sample follow each 
    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
    where the effect from seeing kicks in. 
    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
    are identical in the central region, which indicates similar average seeing 
    conditions.       
    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
    and difference in redshift.
    More importantly, it also suggests that, once the redshift distributions are 
    carefully matched, the difference of \mden{} profile is likely to be physical 
    even in the central region.

\section{D. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering 
    \includegraphics[width=\textwidth]{fig/redbcg_match}
    \caption{
        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
        corresponding to the results shown in the left figure of   
        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
        whose size reflects the $P_{\mathrm{Cen}}$ value.  
        We also color-code them using the richness ($\lambda$) of the host cluster. 
        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
        To further evaluate the matching results, we show the distributions of \mtot{} 
        (middle panel) and redshift (bottom panel) separately. 
        On both panesl, we show the histograms along with their kernel density 
        distributions.  
        And, on the top of each panel, two sets of short vertical lines highlight the median 
        value (solid) and the inter-quartile (dash) of each distribution.~~~
        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
        samples used for the right figure of Fig~\ref{fig:prof_1}.
        The format is exactly the same as the left one, except the \minn{} replaces the 
        \mtot{} in the top and middle panels.}
    \label{fig:match}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
    adjust the value of $N$ to achieve the best match. 
    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
    to split the sample into two redshift bins and match them separately. 
    Typically $N$ is between 3 to 8.
    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
    (Right), and the two samples are well matched in the distributions of \mtot{}
    (or \minn{}) and redshift.  
    For all the comparisons of \mden{} profiles in this work, we match the samples 
    in the same way, and make sure the match has the same quality.

%% ------------------------------------------------------------------------------------ %% 
\section{E. Robustness of the \mden{} Differences} 
	\label{app:robust}

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_2}
      \caption{
          Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
          and higher (right; [11.7, 11.9]) \mtot{} bins. 
          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
          The difference in median profiles is more significant in higher \mtot{} bin.
          }
      \label{fig:prof_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_prof_4}
      \caption{
          Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
          inner region. 
          Left panel shows the results after matching the \minn{} and \meff{} together, 
          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
          \rbcg{} and \nbcg{} galaxies are included.
          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
          }
      \label{fig:prof_4} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure}
      \centering 
      \includegraphics[width=8.5cm]{fig/redbcg_sample_stats_old}
      \caption{
          \textbf{Top-left}: The \logms{}-$g-r$ color relation of the \rbcg{} 
          (red circle; detaield format is the same with the right panel of 
          Fig~\ref{fig:smf1}) and \nbcg{} (grey dots) samples.
          We apply the $k$-corrections from \texttt{iSEDFit} fitting to the colors.~~          
          \textbf{Top-right}: the histograms of the redshift for the \rbcg{} and 
          \nbcg{} galaxies in both \logmtot$>11.2$ and $11.6<$\logmtot{}$<11.9$
          mass bins.
          The vertical lines highlights the $0.3\leq z \leq 0.5$ redshift range.~~
          \textbf{Bottom-left}: the histograms of \mtot{} for the \rbcg{} (orange-red) 
          and \nbcg{} (grey-black) samples at both $z>0.2$ (step-filled histogram) and 
          $0.3 \leq z \leq 0.5$ (stepped histogram). 
          The vertical lines in both top-left and bottom-left figures highlight the 
          $11.6<$\logmtot{}$<11.9$ mass range that will be used in the comparison of 
          the \mtot{}-matched samples.~~
          \textbf{Bottom-right}: the histograms of \minn{} in similar format. 
          Here the vertical lines highlight the 
          $11.2<$\logminn{}$<11.6$ mass range that is used for comparison.
      }
      \label{fig:sample_stats}
  \end{figure}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\begin{figure}
    \centering 
    \includegraphics[width=8.2cm]{fig/redbcg_avg_prof_z}
    \caption{
        Comparison of \mden{} profiles of \rbcg{} (orange-red) and \nbcg{} 
        (grey-black) at $11.6 \le$\logmtot$< 11.9$ in redshift bins of 
        $0.3\leq z<0.4$ (solid lines) and $0.4\leq z<0.5$ (dash lines). 
        We show the individual profile in the background using much thinner line, 
        and highlight the median profiles using thicker line and darker color.
        }
    \label{fig:avg_prof_z}
\end{figure}    
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{B. Comparisons of \mden{} profiles in different redshift bins}
    \label{app:redshift}

@@

    In Fig~\ref{fig:avg_prof_z}, we group the \rbcg{} and \nbcg{} galaxies within 
    $11.6 \le$\logmtot$< 11.9$ into two $z$ bins ($0.3\leq z<0.4$ and $0.4\leq z<0.5$),
    and compare their \mden{} profiles. 
    In two redshift bins, the median \mden{} profiles from the same sample follow each 
    other very well outside 10 kpc, but become visibly different in the central 3-4 kpc,
    where the effect from seeing kicks in. 
    Meanwhile, the median \mden{} profiles of \rbcg{} and \nbcg{} in the same $z$ bin 
    are identical in the central region, which indicates similar average seeing 
    conditions.       
    This confirms that \mden{} profile at $> 5$ kpc is safe from the impacts of seeing 
    and difference in redshift.
    More importantly, it also suggests that, once the redshift distributions are 
    carefully matched, the difference of \mden{} profile is likely to be physical 
    even in the central region.  
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering 
    \includegraphics[width=16cm]{fig/redbcg_match}
    \caption{
        \textbf{Left figure} shows the details of the \mtot{}-matching process, 
        corresponding to the results shown in the left figure of   
        On the top panel, we show the overall distributions of \rbcg{} (light orange boxes) 
        and \nbcg{} (light grey dots) galaxies on the \mtot{}-$z$ plane.  
        And, we match the two sample in the \mtot{}-$z$ space outlined by the shaded region.
        We highlight the \rbcg{} galaxies in this region using bigger boxes in red frames, 
        whose size reflects the $P_{\mathrm{Cen}}$ value.  
        We also color-code them using the richness ($\lambda$) of the host cluster. 
        The matched \nbcg{} galaxies are highlighted using darker color and bigger dots. 
        To further evaluate the matching results, we show the distributions of \mtot{} 
        (middle panel) and redshift (bottom panel) separately. 
        On both panesl, we show the histograms along with their kernel density 
        distributions.  
        And, on the top of each panel, two sets of short vertical lines highlight the median 
        value (solid) and the inter-quartile (dash) of each distribution.~~~
        \textbf{Right figure} shows the similar matching results for the \minn{}-matched
        samples used for the right figure of Fig~\ref{fig:prof_1}.
        The format is exactly the same as the left one, except the \minn{} replaces the 
        \mtot{} in the top and middle panels.}
    \label{fig:match}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=15.5cm]{fig/redbcg_prof_2}
      \caption{
          Comparisons of the \mden{} profiles for \mtot{}-matched \rbcg{} 
          (orange-red) and \nbcg{} (grey-black) galaxies in lower (left; [11.5,11.70]) 
          and higher (right; [11.7, 11.9]) \mtot{} bins. 
          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
          The difference in median profiles is more significant in higher \mtot{} bin.
          }
      \label{fig:prof_2}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=15.5cm]{fig/redbcg_prof_4}
      \caption{
          Comparisons of the \mden{} profiles for \rbcg{} (orange-red) and \nbcg{} 
          (grey-black) galaxies that are matched using the \mstar{} enclosed in the 
          inner region. 
          Left panel shows the results after matching the \minn{} and \meff{} together, 
          and the right panel shows the results when only the \logmtot{}$\ge 11.5$
          \rbcg{} and \nbcg{} galaxies are included.
          Other formats are in consistent with the right figure of Fig~\ref{fig:prof_1}.
          }
      \label{fig:prof_4} 
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\begin{figure*}
    \centering
    \includegraphics[width=16cm]{fig/redbcg_prof_gama_new}
    \caption{
        \textbf{Left:} comparison of \mstar{} estimated by the GAMA survey and 
        the \mtot{} using HSC images in this work. 
        We plot the \logmgama{} against the difference between \logmtot{} and \logmgama{}. 
        The format is very similar to the left panel of Fig~\ref{fig:smf1}. 
        The two vertical lines highlight the mass range $11.4 \leq$\logmgama{}$<11.8$ 
        that is used for the comparison.~~
        \textbf{Right:} we compare the \mden{} profiles of \rbcg{} (orange-red) and 
        \nbcg{} (grey-black) galaxies using the samples matched on the 
        \mgama{}-$z$ plane at $11.4 \leq$\logmgama{}$<11.9$ and $0.28 \leq z < 0.4$. 
        The format is very similar to the ones in Fig~\ref{fig:prof_1}.}
    \label{fig:gama}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{C. Match the \rbcg{} and \nbcg{} samples in \mstar{} and redshift distributions}
    \label{app:match}

@@

    As we only keep the unique \nbcg{} galaxies in the matched sample, we manually 
    adjust the value of $N$ to achieve the best match. 
    When the redshift distribution of the \rbcg{} sample becomes bi-model, we also try 
    to split the sample into two redshift bins and match them separately. 
    Typically $N$ is between 3 to 8.
    In Fig~\ref{fig:match}, we demonstrate this procedure using the results for 
    the \mtot{}-matched (Left) and the \minn{}-matched samples in Fig~\ref{fig:prof_1}
    (Right), and the two samples are well matched in the distributions of \mtot{}
    (or \minn{}) and redshift.  
    For all the comparisons of \mden{} profiles in this work, we match the samples 
    in the same way, and make sure the match has the same quality. 
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{D. Robustness of the \mden{} Differences} 
	\label{app:robust}

@@

    \end{enumerate}
%% ------------------------------------------------------------------------------------ %%

%% ------------------------------------------------------------------------------------ %% 
\section{E. Comparison of \mden{} profiles using \mstar{} from the GAMA survey}
    \label{app:gama}
